Quality Definitions of Qualities

### 2021-10-10 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added abstraction definitions

>>>>

\begin{defn}
Abstraction refers to the process of removing irrelevant details in order to focus on the essential parts of the system \citep{filipovikj2017pattern}.
\end{defn}

\begin{defn}
Abstraction is a special case of separation of concerns wherein we separate the concerns of the important aspects from the concern of the less important details \citep{GhezziEtAl2003}.
\end{defn}

\begin{defn}
An abstraction is a simplification of some complex element of a system used to communicate meaning in a single phrase \citep{roger2015software}.
\end{defn}
